
\cvsection{SKILLS}
\begin{itemize}
\item \textbf{Programming/Scripting Languages}: Python, C, C++, JavaScript
\item \textbf{Front-end}: HTML, CSS, Bootstrap,Angular 7
\item \textbf{Back-end}: Django, Django Rest Framework
\item \textbf{Database}: SQLite3, MySQL,postgresql
\item \textbf{Operating Systems}: Microsoft Windows, Linux
\item \textbf{Others}: Celery,Redis,Ngnix,BeautifulSoup, Scrappy, Git, AWS-EC2, S3, RDS
\end{itemize}
%\cvskill{German}{3}

% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Know your restaurants}
\begin{itemize}
\item Developed a restaurants finder and locator webapp in GeoDjango that uses Geospatial data of restaurants using Zomato API.
\item Further helps user to locate the nearby restaurants,Used celery and redis for optimization of restaurants searches.
\end{itemize}
\smallskip
\cvproject {LetsShare}
\begin{itemize}
\item A Single page application for users to share files with each other.
\item Used: Angular7, Djangorestframework, JWT.
\end{itemize}
\smallskip
\cvproject{Attendance Notifier}
\begin{itemize}
\item  A Notification API for attendance by sending the SMS to the users with the subjects. 
\item Used Django, Celery, Redis, Crontab.Deployed on AWS using Ngnix , Gunicorn and Supervisord.
\end{itemize}
\smallskip
\cvproject{Code Differentiator}
\begin{itemize}
\item A single page application in Django to check the similarities and differences between two c or c++ codes. 
\item Complied and compared the program using BASH Script.
\end{itemize}
\smallskip
\cvproject{Competitive Programming Helper}
\begin{itemize}
\item Written in Python powered by Django, this system is developed during Codechef API hackathon.
\item Used to find hidden testcases between a bruteforce and a optimized program
\item Other features include a testcase Generator for generating random test cases.
\end{itemize}
{}

\cvsection{Achievements}
\begin{itemize}
    \item \textbf{Secured 10 Rank} in ‘Codechef API Hackathon' powered by alibaba Cloud
    \item \textbf{Secured 9863 Rank} in ‘Smackdown 2017' codechef's annual multi round programming competition
\end{itemize}